
\documentclass{sig-alternate}

\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{times}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}
\usepackage{float}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{alltt}
\usepackage{color}
\usepackage{textcomp}
\usepackage{balance}

\bibpunct{[}{]}{,}{n}{}{}

\newcommand{\ie}{\textit{i.e.,} }
\newcommand{\eg}{\textit{e.g.,} }

\def\denseitems{
  \itemsep1pt plus1pt minus1pt
  \parsep0pt plus0pt
  \parskip0pt\topsep0pt}

\begin{document}

\conferenceinfo{FOSE}{'14, May 31 -- June 7, 2014, Hyderabad, India}
\CopyrightYear{2014}
\crdata{978-1-4503-2865-4/14/05}

\title{Software Services: A Research Roadmap}

\numberofauthors{4}

\author{
\alignauthor Satish Chandra\titlenote{\small This author was formerly at IBM.}\\
       \affaddr{Samsung Electronics}\\
       \affaddr{San Jose, CA}\\
       \email{schandra@acm.org}
\alignauthor Vibha S Sinha\\
	\affaddr{IBM Research}\\
	\affaddr{New Delhi, India}\\
	\email{vibha.sinha@in.ibm.com}
\and
\alignauthor Saurabh Sinha\\
	\affaddr{IBM Research}\\
	\affaddr{Bangalore, India}\\
	\email{saurabhsinha@in.ibm.com}
\alignauthor Krishna Ratakonda\\
	\affaddr{IBM T J Watson Research}\\
	\affaddr{Yorktown Heights, NY}\\
	\email{ratakond@us.ibm.com}
}

\maketitle

\begin{abstract}

Software services companies offer software development, testing and maintenance
as a ``service'' to other organizations.  As a thriving industry in its own
right, software services offers certain unique research problems as well as
different takes on research problems typically considered in software
engineering research. In this paper, we highlight some of these research
problems, drawing heavily upon our involvement with IBM Global Business Services
organization over the past several years.  We focus on four selected topics: how
to organize people and the flow of work through people, how to manage knowledge
at an organizational level, how to estimate and manage risk in a services
engagement, and finally, testing services. These topics by no means cover all
areas pertinent to software services; rather, they reflect ones in which we have
personal perspectives to offer.  We also share our experience in deployment of
research innovations in a large service delivery organization.

\end{abstract}

\category{D.2.9}{Software Engineering}{Management}
\category{D.2.5}{Software Engineering}{Testing and Debugging}

\terms{Management, Measurement}

\keywords{Software services, distributed development, testing, knowledge management, risk management}

\input{intro}
\input{kinds}

\input{global}
\input{km_new}
%\input{trouble}
\input{risk}
\input{testing}
\input{experience}

\section{Conclusion}
\label{sec:conclusion}

Software services companies rely crucially innovations in individual and
organizations productivity for their competitiveness. In this paper, we examined
some of the topics that require attention from the software engineering research
community. We examined challenges in how modern services companies organize
their work and workforce; challenges in knowledge management at an organization
level; issues in risk assessment; and finally challenges in testing services. We
also discusses challenges in deployment of research innovations in real-world
services context. We hope that the research community takes a careful look at
the software services industry for many opportunities for impact.

\section*{Acknowledgements}
The research agenda presented in this paper is a collation of knowledge the
authors and various other IBM Researchers accumulated in course of working with
IBM's service delivery practitioners. From services delivery, we would like to
thank Anup K Ghosh, Jack Bisceglia, and Achin K Das for sharing the IT delivery
challenges and championing the use of research tools in their teams. At IBM
Research, we would like to thank Sugata Ghosal, Manish Gupta, and Rakesh Mohan
for driving the services delivery research agenda. We would also like to
acknowledge our colleagues Min Chee, Pankaj Dhoolia, Richard Goodwin, Juhnyoung
Lee, Debapriyo Majumdar, Senthil Mani, Pietro Mazzoleni, Debdoot Muk\-herjee,
Diptikalyan Saha, Karthik Sankaranarayanan, Bikram Sengupta, Renuka Sindhgatta,
Suresh Thummalapenta, and Joe Zhou, who have been involved in various research
initiatives during course of which the challenges listed in this paper were
identified.

\bibliographystyle{abbrvnat}
{\small
%\balance
\bibliography{fose,risk-global,km}
}

\end{document}
