\section{Introduction}
\label{sec:intro}

Software development is most visibly associated with companies that manufacture
software products.  Corporate names such as Microsoft, Google, IBM, SAP, Oracle,
and so on are well-known software companies.  These companies offer several
software products to individual consumers and businesses.

In the broader information technology ecosystem, software development is also
associated with ``services companies.''  Instead of offering software products,
these companies develop, test, and maintain software for other businesses, \ie
they offer software engineering as a service.\footnote{\small Not to be confused
  with software-as-a-service, which is a way to deliver software products.}
Examples of service companies include Accenture, Cap Gemini, Infosys, Atos, and
so on; in addition, companies such as IBM and HP have a large services business
in addition to their software and hardware businesses.

There are two main drivers for demand for software services.  First, most
businesses prefer to focus on their core competence, rather than develop and
foster in house competence for software development.  For example, every company
in the financial sector relies heavily on information technology, but
information technology is not the basis on which they differentiate themselves
in that sector. They prefer not to run large in-house teams that have expertise
in ever growing set of software technologies, when they can easily procure IT
services on demand from service companies. Obviously, some number of in-house
staff is always needed, but the bulk of work can be outsourced to service
companies.

Second, although a lot of business software functionality is now available in
pre-packaged applications, it is not realistic to run an enterprise entirely
with off-the-shelf software. Significant custom\-ization and systems integration
is required to run any large enterprise, even if substantial building blocks are
available off the shelf. Moreover, custom software must be maintained to
incorporate new business needs or to accommodate legislative compliance, and
continually upgraded to newer technologies such as cloud. Service companies have
deep industry as well as technology expertise to cater to these needs. The fact
that services companies can also deliver services cost effectively using a large
pool of global resources is an added benefit.

Like software product companies, services companies employ software engineers in
large numbers, and take on long-running software projects. Given the scale of
operations, many of the usual challenges in software engineering that are well
known in product development also apply in the context of services.  However,
the two kinds of businesses have some differences, due to which certain
challenges become more pronounced for services companies.

The most salient of differences is this: product companies compete in the market
they serve on the basis of the features offered in their product and how well it
anticipate their customers' needs. Thus, their main focus is on innovation in
identifying features that their customers would be willing to pay for, and
bringing out a product that offer those features before their competition
does. By contrast, services companies do not compete on the basis of the
features of any product; rather they compete in terms of the ``quality of
service'' that they offer to the business that purchase their services. Here,
quality of service informally means several things that one may associate with
any kind of services business, even outside of information technology: can the
service provider deliver on their contract on time, with acceptable work
quality, and at a competitive price.  Therefore, the innovation in service
companies pertains to techniques for carrying out projects reliably, on time,
with acceptable quality, and managing the cost.

Another important difference is that in product companies, copies of the same
product are sold to a large number of customers and, typically, the transaction
is one-time payment of license fee.  A services company provides services to a
much smaller number of clients, and the transaction is an ongoing relationship
rather than a one-time payment of license fee. This has an important bearing on
deployment of innovation.  A product company must be extremely careful in
choosing what innovations to productize because they cannot afford to get it
wrong; however, if successfully shipped, the innovation automatically makes its
way to a large number of users.  In a services company, deploying innovation is
somewhat less risky, but it does not scale automatically: it can take just as
much work in rolling out an innovation to the next client as it did for the
first client.

%% A third difference is in the timeline of engagement with the customer.

%% The global market for software services is almost the same size as the market for software products in terms of revenues.

In this paper, we consider selected directions for research in software
engineering that would impact how software services are delivered.  The topics
we have chosen are influenced by our work during the past few years at IBM;
there are numerous other topics that would be fruitful areas of research.  Some
topics of current prominence that are not considered in this paper include
legacy transformation, API identification and extraction, and migration of
applications to cloud.

%% There are numerous other topics, e.g. legacy transformation and cloud migration that are very promising areas of research.

The rest of the paper is organized as follows. In the next section, we take a
closer look at a sample software services engagement.  Section~\ref{sec:global}
describes the research challenges in how people and work are organized in a
large services engagement.  Section~\ref{sec:km} examines the problems and
challenges in knowledge management in the context of software services.
Section~\ref{sec:risk} describes challenges in risk prediction.
Section~\ref{sec:testing-debugging} takes a closer look at testing services, in
which the objective of the engagement is to outsource testing activities.  In
Section~\ref{sec:experience}, we relate our experiences in deploying innovations
in industrial service delivery; finally, Section~\ref{sec:conclusion} concludes
the paper.

